A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-28 asc.tex
Fix typos and minor mistakes

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi.png}
			\caption{Base mesh}
			\label{fig:problem_geometry:base_mesh}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi.png}
			\caption{MMCs}
			\label{fig:problem_geometry:mmcs}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi.png}
			\caption{MOF reconstruction}
			\label{fig:problem_geometry:mof}
		\end{subfigure}
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi_refined.png}
		\end{subfigure}
		\caption{The figure illustrates global unstructured polyhedral mesh (left); Physical interfaces for three materials and cut cells, i.e. multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment-of-fluid method (right). Everything is shown for two refinement level of the base mesh \label{fig:problem_geometry}}
	\end{figure}

	We assume the triangulation  $\bmesh$ of $\Omega$ consisting of general polyhedral elements as illustrated in Figure~\ref{fig:problem_geometry} (left). This triangulation constitutes our macro-mesh. The material interfaces, i.e. surfaces where $\vect K$ may experience discontinuities, may cut through the macro-mesh in an arbitrary way; see Figure~\ref{fig:problem_geometry} (center). The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called Multi-Material Cells (MMCs). In practice,  we are given a reconstructed interface by a volume-of-fluid or moment-of-fluid method. This reconstructed interface may be discontinuous across faces of MMC, but locally within each ${\bcell \in \bmesh}$ it is a collection of planar surfaces; see Figure~\ref{fig:problem_geometry} (right).

@@

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on all the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$. We set~$\bfaces_\bcell \subset \bfaces$ to be the subset of macro-faces forming the boundary of a cell~$T$. With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of d.o.f. are
	\[
		n_\bcell = \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
		n_\bmesh = \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
	\]
	respectively.

@@

	\begin{figure}[h]
		\centering		
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_1.pdf_tex}
			\caption{$\nu_F = 1$}%,
			\label{fig:asc_dofs:asc1:pc}
		\end{subfigure}%
		\qquad\quad
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_2.pdf_tex}
			\caption{$\nu_F = 3$}		
		\end{subfigure}
		\caption{$\lambda_{ji}(\mmesh)$ are local d.o.f. used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda_j(T)$, $\lambda'_j(T)$ are global d.o.f. used to describe mortar space $\Lambda$. Left: Face $F$ is single-material and uses one global d.o.f.; Right: Face $F$ is multi-material and uses two global d.o.f.
		\label{fig:asc_dofs:asc1:mmc}}
	\end{figure}

@@

	Now we show that the global matrix~$\vect S_\bmesh$ in~\eqref{asc_system} is symmetric and positive definite. We give the arguments for ASC(1). Same arguments hold for ASC(0) after obvious simplifications.
	%\begin{theorem}\label{thm:asc0}
	%		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(0)
	%	\end{theorem}
	%	\begin{proof}
	%		From~\eqref{asc0_interp} we have that for any cell~$\bcell$\,/\,its mini\,mesh~$\mmesh$ the interpolating matrix may be written as
	%		\begin{equation*}
	%			\vect R_\mmesh =
	%			\begin{pmatrix}
	%				{\vect e}_1 & & & \\
	%				& {\vect e}_2 & & \\
	%				& & \ddots & \\
	%				& & & {\vect e}_m
	%			\end{pmatrix},
	%		\end{equation*}
	%		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and ${\vect e}_k \coloneqq$ column vector of all ones; its length is the number of mini\,faces of the base\,face~$k$. Clearly, columns of~$\vect R_\mmesh$ are linearly independent.
	%		
	%	\end{proof}
	\begin{lemma}\label{thm:asc1}
		%If~$\bfaces_\bcell \cap \bfaces[\textnormal{mixed}] = \varnothing$, then~
		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(1)
	\end{lemma}
	\begin{proof}
		\vskip -.3cm
		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
		%that has no mixed base\,faces, ${\bfaces_\bcell \cap \bfaces[mixed] = \varnothing}$,
		the interpolating matrix may be written as
		\begin{equation}\label{r_wo_mixed}\footnotesize
			\vect R_\mmesh =
			\begin{pmatrix}
				\vect S_1 & & & \\
				& \vect S_2 & & \\
				& & \ddots & \\
				& & & \vect S_m
			\end{pmatrix},
		\end{equation}
		where~$m \coloneqq$ number of macro-faces spanning~$\bcell$ and
		\begin{equation*}
			\vect S_k \coloneqq
			\begin{cases}
				\begin{pmatrix}
					1 &  s_{k\,1} \\
					\vdots & \vdots \\
					1 &  s_{k\,m_k} \\
				\end{pmatrix}, & \text{if }k\text{th face is multi-material face}, \\
				1, & \text{otherwise},
			\end{cases}
		\end{equation*}
		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th macro-face. If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.

@@

		Now we show the positive definiteness of $\vect S_\bmesh$ if $|\partial\Omega_D|>0 $. Consider  any given $\bcell\in\bmesh$.
		Matrix  $\vect A_{\mmesh}$ defines the discrete Dirichlet-to-Neumann map for $\partial\bcell$.
		If $\partial\bcell\cap\partial\Omega_D$, then $\Ker \vect A_{\mmesh} = \{\vect 0\}$. Otherwise $\Dim\big(\Ker \vect A_{\mmesh}\big) = 1$ and $\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect\lambda_\mmesh=0$ implies that $\vect\lambda_\mmesh$ is constant on $\partial\bcell$. Consider some $\lambda$ from the mortar space $\Lambda$ and corresponding vector of moments  $\vect \lambda_\bmesh$. Using connectivity of the mesh one easily finds that $\vect R_\mmesh\,\vect\lambda_\bcell$ can be constant on every $T\in\bmesh$ only if $\lambda$ is constant. Due to the assumption $|\partial\Omega_D|>0$ this implies $\lambda=0$.
		% Thus we have
		%		\begin{equation*}
		%			\big(\vect S_\bcell\,{\vect x},\,{\vect x}\big) =
		%			\big(\vect R^T_\mmesh \left( \vect C_{\mmesh}\,\vect A_{\mmesh}\,\vect C_{\mmesh} \right) \vect R_\mmesh\,{\vect x},\,{\vect x} \big) =
		%			\big(\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x},\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x} \big) \ge 0
		%		\end{equation*}
		%		for all~$\bcell \in \bmesh$ and
		%		\begin{equation*}
		%			\big(\vect S_\bcell\,{\vect x},\,{\vect x} \big) > 0
		%		\end{equation*}
		%		for some~$\bcell \in \bmesh$ since~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$. So
		Hence for any $\vect0\neq\vect\lambda_\bmesh\in \mathbb{R}^{n_\bmesh}$ we have
		\begin{align*}
		\left(\vect S_\bmesh\,\vect\lambda_\bmesh,\,\vect\lambda_\bmesh\right) &\stackrel{\eqref{global_system_assembly}}{=}
		\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\vect\lambda_\bmesh},\,{\vect\lambda_\bmesh} \Big) =
		\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\vect\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\vect\lambda_\bmesh}}_{{\vect \lambda_\bcell} \coloneqq} \big) \\
		& = \sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect \lambda_\bcell},\,{\vect \lambda_\bcell} \big) > 0.
		\end{align*}
		The last inequality holds, since there exists $\bcell$ such that $\vect \lambda_\bcell=\vect N_\bcell\,{\vect\lambda_\bmesh}$ is not in the kernel for $\vect\lambda_\bmesh\neq\vect0$.
	\end{proof}

>>>>

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi.png}
			\caption{Macro-mesh}
			\label{fig:problem_geometry:base_mesh}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi.png}
			\caption{MMCs}
			\label{fig:problem_geometry:mmcs}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi.png}
			\caption{MOF reconstruction}
			\label{fig:problem_geometry:mof}
		\end{subfigure}
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_base_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mmcs_voronoi_refined.png}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{ring_mini_voronoi_refined.png}
		\end{subfigure}
		\caption{The figure illustrates global unstructured polyhedral mesh (left); Physical interfaces for three materials and cut cells, i.e. multi-material cells (central); The piecewise-planar discontinuous reconstruction of the interfaces by the moment-of-fluid method (right). Everything is shown for two refinement level of the macro-mesh \label{fig:problem_geometry}}
	\end{figure}

	We assume the triangulation  $\bmesh$ of $\Omega$ consisting of general polyhedral elements as illustrated in Figure~\ref{fig:problem_geometry} (left). This triangulation constitutes our macro-mesh. The material interfaces, i.e. surfaces where $\vect K$ may experience discontinuities, may cut through the macro-mesh in an arbitrary way; see Figure~\ref{fig:problem_geometry} (center). The polygonal cells ${\bcell \in \bmesh}$ cut by the interfaces are further called multi-material cells (MMCs). In practice,  we are given a reconstructed interface by a volume-of-fluid or moment-of-fluid method. This reconstructed interface may be discontinuous across faces of MMCs, but locally within each ${\bcell \in \bmesh}$ it is a collection of planar surfaces; see Figure~\ref{fig:problem_geometry} (right).

@@

	Since the continuity of flux condition \eqref{flux_cond} and boundary conditions are enforced on all the \emph{external} edges of $T$, we need to distinct the vector ${\vect u}^\text{ext}_\mmesh$ of fluxes on $\mfaces[ext](T)$, which is just a trivial restriction of ${\vect u}_\mmesh$ on the edges  from $\mfaces[ext](T)$,
	\begin{equation}\label{system_mini}
		{\vect u}^\text{ext}_\mmesh \coloneqq \vect E_\mmesh^T\,{\vect u}_\mmesh,
	\end{equation}
	where $\vect E_\mmesh^T$ is the restriction matrix with entries equal $0$ or $1$.

@@

	For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$. We set~$\bfaces_\bcell \subset \bfaces$ to be the subset of macro-faces forming the boundary of a cell~$T$. With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of d.o.f. are
	\[
		n_\bcell \coloneqq \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
		n_\bmesh \coloneqq \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
	\]
	respectively.

@@

	\begin{figure}[h]
		\centering		
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_1.pdf_tex}
			\caption{$\nu_F = 1$}%,
			\label{fig:asc_dofs:asc1:pc}
		\end{subfigure}%
		\qquad\quad
		\begin{subfigure}{.45\linewidth}
			\centering
			\svginputw{e_plus_2.pdf_tex}
			\caption{$\nu_F = 3$}		
		\end{subfigure}
		\caption{$\lambda_{ji}(\mmesh)$ are local d.o.f. used in MFD for $\lambda$ from \eqref{dual_mini}, $\lambda^{(0)}_j(T)$, $\lambda^{(1)}_j(T)$ are global d.o.f. used to describe mortar space $\Lambda$. Left: Face $F$ is single-material and uses one global d.o.f.; Right: Face $F$ is multi-material and uses two global d.o.f.
		\label{fig:asc_dofs:asc1:mmc}}
	\end{figure}

@@

	Now we show that the global matrix~$\vect S_\bmesh$ in~\eqref{asc_system} is symmetric and positive definite. We give the arguments for ASC(1). Same arguments hold for ASC(0) after obvious simplifications.
	\vskip .2cm
	%\begin{theorem}\label{thm:asc0}
	%		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(0)
	%	\end{theorem}
	%	\begin{proof}
	%		From~\eqref{asc0_interp} we have that for any cell~$\bcell$\,/\,its mini\,mesh~$\mmesh$ the interpolating matrix may be written as
	%		\begin{equation*}
	%			\vect R_\mmesh =
	%			\begin{pmatrix}
	%				{\vect e}_1 & & & \\
	%				& {\vect e}_2 & & \\
	%				& & \ddots & \\
	%				& & & {\vect e}_m
	%			\end{pmatrix},
	%		\end{equation*}
	%		where~$m \coloneqq$ number of base\,faces spanning~$\bcell$ and ${\vect e}_k \coloneqq$ column vector of all ones; its length is the number of mini\,faces of the base\,face~$k$. Clearly, columns of~$\vect R_\mmesh$ are linearly independent.
	%		
	%	\end{proof}
	\begin{lemma}\label{thm:asc1}
		%If~$\bfaces_\bcell \cap \bfaces[\textnormal{mixed}] = \varnothing$, then~
		$\Ker\vect R_\mmesh = \{ {\vect 0} \}$ for ASC(1)
	\end{lemma}
	\begin{proof}
		\vskip -.3cm
		From~\eqref{asc1_interp} we have that for any cell~$\bcell$ and its mini-mesh~$\mmesh(T)$
		%that has no mixed base\,faces, ${\bfaces_\bcell \cap \bfaces[mixed] = \varnothing}$,
		the interpolating matrix may be written as
		\begin{equation}\label{r_wo_mixed}\footnotesize
			\vect R_\mmesh =
			\begin{pmatrix}
				\vect S_1 & & & \\
				& \vect S_2 & & \\
				& & \ddots & \\
				& & & \vect S_m
			\end{pmatrix},
		\end{equation}
		where~$m \coloneqq$ number of macro-faces spanning~$\bcell$ and
		\begin{equation*}
			\vect S_k \coloneqq
			\begin{cases}
				\begin{pmatrix}
					1 &  s_{k\,1} \\
					\vdots & \vdots \\
					1 &  s_{k\,m_k} \\
				\end{pmatrix}, & \text{if }k\text{th face is multi-material face}, \\
				1, & \text{otherwise},
			\end{cases}
		\end{equation*}
		$1 < m_k$ is the number of mini-faces of the~$k$th macro-face, $ s_{k\,i}$ is the signed distance between centroids of~$i$th mini-face and~$k$th macro-face. If~$\bcell$ contains only one material, then $\vect R_\mmesh = \vect I$ and hence $\Ker\vect R_\mmesh = \{ {\vect 0} \}$, so we assume that there is at least one multi-material  face.

@@

		Now we show the positive definiteness of $\vect S_\bmesh$ if $|\partial\Omega_D|>0 $. Consider  any given $\bcell\in\bmesh$.
		Matrix  $\vect A_{\mmesh}$ defines the discrete Dirichlet-to-Neumann map for $\partial\bcell$.
		If $\partial\bcell\cap\partial\Omega_D$, then $\Ker \vect A_{\mmesh} = \{\vect 0\}$. Otherwise $\Dim\big(\Ker \vect A_{\mmesh}\big) = 1$ and $\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect\lambda_\mmesh=0$ implies that $\vect\lambda_\mmesh$ is constant on $\partial\bcell$. Consider some $\lambda$ from the mortar space $\Lambda$ and corresponding vector of moments  $\vect \lambda_\bmesh$. Using connectivity of the mesh one easily finds that $\vect R_\mmesh\,\vect\lambda_\bcell$ can be constant on every $T\in\bmesh$ only if $\lambda$ is constant. Due to the assumption $|\partial\Omega_D|>0$ this implies $\lambda=0$.
		% Thus we have
		%		\begin{equation*}
		%			\big(\vect S_\bcell\,{\vect x},\,{\vect x}\big) =
		%			\big(\vect R^T_\mmesh \left( \vect C_{\mmesh}\,\vect A_{\mmesh}\,\vect C_{\mmesh} \right) \vect R_\mmesh\,{\vect x},\,{\vect x} \big) =
		%			\big(\vect A_{\mmesh}\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x},\,\vect C_{\mmesh}\,\vect R_\mmesh\,{\vect x} \big) \ge 0
		%		\end{equation*}
		%		for all~$\bcell \in \bmesh$ and
		%		\begin{equation*}
		%			\big(\vect S_\bcell\,{\vect x},\,{\vect x} \big) > 0
		%		\end{equation*}
		%		for some~$\bcell \in \bmesh$ since~$\Ker\vect R_\mmesh = \{ {\vect 0} \}$. So
		Hence for any $\vect0\neq\vect\lambda_\bmesh\in \mathbb{R}^{n_\bmesh}$ we have
		\begin{align*}
		\left(\vect S_\bmesh\,\vect\lambda_\bmesh,\,\vect\lambda_\bmesh\right) &\stackrel{\eqref{global_system_assembly}}{=}
		\Big( \big( \sum_{\bcell \in \bmesh} \vect N^T_\bcell\,\vect S_\bcell\,\vect N_\bcell \big){\vect\lambda_\bmesh},\,{\vect\lambda_\bmesh} \Big) =
		\sum_{\bcell \in \bmesh} \big( \vect S_\bcell\,\vect N_\bcell\,{\vect\lambda_\bmesh},\,\underbrace{\vect N_\bcell\,{\vect\lambda_\bmesh}}_{{\vect \lambda_\bcell} =} \big) \\
		& = \sum_{\bcell \in \bmesh} \big(\vect S_\bcell\,{\vect \lambda_\bcell},\,{\vect \lambda_\bcell} \big) > 0.
		\end{align*}
		The last inequality holds, since there exists $\bcell$ such that $\vect \lambda_\bcell=\vect N_\bcell\,{\vect\lambda_\bmesh}$ is not in the kernel for $\vect\lambda_\bmesh\neq\vect0$.
	\end{proof}
